% =====================================================================
%  TITLE PAGE
% =====================================================================
\begin{titlepage}
\thispagestyle{empty}
\vspace*{1.4cm}

{\Huge\bfseries\color{Slate} Predicting India's Weighted\\Average Call Money Rate\par}
\vspace{0.45em}
{\Large\color{Slate} An End-to-End Data Science Project on RBI NDAP and\\Market Data, with a Live Dashboard, Counterfactual Simulator,\\and AI-Powered Data Agent\par}

\vspace{1.0em}
{\large\bfseries Aamer Jalan and Arnav Goyal\par}
{\large Ashoka University, Data Science and Management\par}
{\normalsize \today\par}

\vspace{1.2em}
\noindent\textbf{\color{Slate}Summary.}
This report documents an end-to-end data science investigation into the
Weighted Average Call Money Rate (WACMR), the operational target of the
Reserve Bank of India's (RBI) Liquidity Adjustment Facility and the
cleanest market-revealed signal of overnight rupee liquidity. Ten
public datasets were ingested, eight from the NDAP open-data API and
two from Yahoo Finance, then aligned onto a canonical Friday weekly
grid spanning February 2014 to July 2024. The resulting panel of 545
observations across 117 features was stored in SQLite and analysed
through three complementary lenses, namely unsupervised regime
discovery via PCA and K-Means, supervised forecasting via walk-forward
XGBoost with SHAP interpretability, and a domain-curated NLP corpus of
seventy-five RBI policy events. The findings are deployed as a live,
publicly accessible web application that includes a policy
counterfactual simulator and a Gemini-powered data agent.

\vspace{0.6em}
\noindent\textbf{\color{Slate}Project highlights.}
\begin{center}
\statcard{545}{weeks of weekly\\macro data}\hfill
\statcard{117}{engineered\\features}\hfill
\statcard{10}{data\\sources}\hfill
\statcard{70.9\%}{directional\\accuracy}\hfill
\statcard{75}{curated\\policy events}
\end{center}

\vspace{0.8em}
\noindent
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\linewidth}{@{}p{0.32\linewidth} Y@{}}
\toprule
\rowcolor{SoftGray}\textbf{\color{Slate}Data scope} &
February 2014 to July 2024, weekly Friday-aligned panel,
545 rows by 119 columns in SQLite, target variable
\texttt{target\_wacmr} (RBI \texttt{rates\_I7496\_26}). \\
\rowcolor{TealTint}\textbf{\color{Slate}Analytical methods} &
PCA with 90.4\% variance retention (14 components), K-Means with K=2 (silhouette 0.4238),
walk-forward expanding-window XGBoost over 389 test steps, SHAP
TreeExplainer, and a manually curated NLP event corpus. \\
\rowcolor{SoftGray}\textbf{\color{Slate}Headline result} &
Baseline XGBoost achieves RMSE 0.1019 (about ten basis points) and 70.9\%
directional accuracy. None of 28 equity and forex features rank in the
top 15 SHAP drivers, confirming that WACMR is purely corridor-bound at
the weekly horizon. \\
\rowcolor{TealTint}\textbf{\color{Slate}Live system} &
Next.js front-end on Vercel, FastAPI backend on Render, Gemini 2.5 Flash
function-calling agent over the dataset, and a real-time policy
counterfactual slider with cached inference (26 seconds compressed to
roughly 50 ms). \\
\bottomrule
\end{tabularx}

\vspace{1.0em}
\noindent\textbf{\color{Slate}Public deployment.}\\[2pt]
\noindent\hspace{0.3em}\textbf{Dashboard and blog:} \url{https://dsm-project-phi.vercel.app}\\
\noindent\hspace{0.3em}\textbf{API and agent:} \url{https://wacmr-api.onrender.com}\\
\noindent\hspace{0.3em}\textbf{Source repository:} \url{https://github.com/AJ112103/DSM_project}

\vfill
\noindent\textit{\small \color{Slate} All figures cited in this report are reproducible from the
code committed to the repository. Pipeline stages are numbered
\texttt{stage1\_*} through \texttt{stage6\_*} and are idempotent.}
\end{titlepage}

% TOC on page 2
\setcounter{page}{2}
\hypersetup{linkcolor=Slate}
{\color{Slate}\tableofcontents}
\hypersetup{linkcolor=Teal}
\clearpage
